Where Do Population III Stars Form?

### 2018-10-24 paper.tex
removing files

Numerical simulations have also been employed to investigate collapse thresholds and Pop III star formation. \citet[hereafter M01]{Machacek01} found similar results to those mentioned previously, in that the LW feedback can suppress the collapse of small mass halos. They derive a simple analytic expression for the mass threshold of halos given a particular LW flux:
\begin{equation} \label{mthresh}
	M_{TH} ( M_{\odot} ) = 1.25 \times 10^{5} + 8.7  \times 10^{5} \left( \frac{4 \pi J_{LW}}{10^{-21}} \right)^{.47}
\end{equation}
We will compare our results with this relation in future sections. \citet{yoshida03} also finds that cooling is inefficient in halos with a LW background > 0.01, although with sufficient \hh{} shielding, halos are able cool in the given LW background radiation. In fact, \citet{Wise07_UVB} found that central shocks drive \hh{} formation, allowing the halo to cool in a LW background flux of 10$^{-20}$. They find that \hh{} cooling is always a dominant process, even in large LW background fluxes. Assisting this result, \citet{OShea08} find that Pop III star formation can occur in relatively high LW backgrounds, implying that the LW background may not be a complete indicator of whether or not Pop III stars will form in a given halo.

@@

Binning the data in $\Delta z$ = 1, the mean halo mass hosting Pop III stars is determined, and plotted against the redshift bins in Figure \ref{fig:mean_mass}. Equation \ref{mthresh} is plotted using the LW background intensity in Eq. \ref{LWbg}. Notably, the mean halo mass falls well below the relation until $z$ = 12.5. Below the mass threshold, the mean halo mass is 10$^{5.89}$ M$_{\odot}$, and rises to 10$^{6.6}$ M$_{\odot}$ after $z$ = 12.5. The large discrepancy between our data and the mass threshold from M01 is indicative of the \hh{} shielding which is included in our simulation. \hh{} shielding allows for halos to form at much lower masses, and therefore, Pop III stars are forming in these halos at early times. In the analysis done in M01, \hh{} shielding is neglected in their calculations for a variety of reasons, including the Doppler broadening of LW bands and large column densities of \hh{} only beginning to form at late times. Interestingly, a full radiative transfer simulation, such as ours, does not produce identical results as M01 predicts. Throughout the literature, there appears to be a consensus that \hh{} self-shielding will help smaller mass halos collapse in the presence of a LW background radiation \citep[e.g.]{yoshida03, Ricotti01, Glover01, Hartwig15}.

\begin{figure}
	\includegraphics[width=\columnwidth]{images/mean_mass_errorb_fix.pdf}
    \caption{For halos hosting new Pop III stars, the mean halo mass for redshift bins of $\Delta z$ = 1 is plotted along the left hand side versus redshift. The black scatter points indicate the mean halo mass for that redshift bin and the x indicate the median halo mass. The error bars indicate the 15.1\% and 84.1\% percentiles. Plotted along the right hand side is the percentage of halos that fall below the M01 mass threshold, also plotted along redshift. The M01 mass threshold (Eq. \ref{mthresh}), is plotted for the constant LW background in Eq. \ref{LWbg}. Almost all halos fall below the M01 relation, until $z$ = 12.5, when the mean halo mass rises above the relation.}
    \label{fig:mean_mass}
\end{figure},

>>>>

Numerical simulations have also been employed to investigate collapse thresholds and Pop III star formation. \citet[hereafter M01]{Machacek01} found similar results to those mentioned previously, in that the LW feedback can suppress the collapse of small mass halos. They derive a simple analytic expression for the mass threshold of halos given a particular LW flux:
\begin{equation} \label{mthresh}
	M_{TH} ( M_{\odot} ) = 1.25 \times 10^{5} + 8.7  \times 10^{5} \left( \frac{4 \pi J_{LW}}{10^{-21}} \right)^{.47}
\end{equation}
We will compare our results with this relation in future sections. \citet{Yoshida03} also finds that cooling is inefficient in halos with a LW background > 0.01, although with sufficient \hh{} shielding, halos are able cool in the given LW background radiation. In fact, \citet{Wise07_UVB} found that central shocks drive \hh{} formation, allowing the halo to cool in a LW background flux of 10$^{-20}$. They find that \hh{} cooling is always a dominant process, even in large LW background fluxes. Assisting this result, \citet{OShea08} find that Pop III star formation can occur in relatively high LW backgrounds, implying that the LW background may not be a complete indicator of whether or not Pop III stars will form in a given halo.

@@

Binning the data in $\Delta z$ = 1, the mean halo mass hosting Pop III stars is determined, and plotted against the redshift bins in Figure \ref{fig:mean_mass}. Equation \ref{mthresh} is plotted using the LW background intensity in Eq. \ref{LWbg}. Notably, the mean halo mass falls well below the relation until $z$ = 12.5. Below the mass threshold, the mean halo mass is 10$^{5.89}$ M$_{\odot}$, and rises to 10$^{6.6}$ M$_{\odot}$ after $z$ = 12.5. The large discrepancy between our data and the mass threshold from M01 is indicative of the \hh{} shielding which is included in our simulation. \hh{} shielding allows for halos to form at much lower masses, and therefore, Pop III stars are forming in these halos at early times. In the analysis done in M01, \hh{} shielding is neglected in their calculations for a variety of reasons, including the Doppler broadening of LW bands and large column densities of \hh{} only beginning to form at late times. Interestingly, a full radiative transfer simulation, such as ours, does not produce identical results as M01 predicts. Throughout the literature, there appears to be a consensus that \hh{} self-shielding will help smaller mass halos collapse in the presence of a LW background radiation \citep[E.g.]{Yoshida03, Ricotti01, Glover01, Hartwig15}.

\begin{figure}
	\includegraphics[width=\columnwidth]{images/mean_mass_errorb_fix.pdf}
    \caption{For halos hosting new Pop III stars, the mean halo mass for redshift bins of $\Delta z$ = 1 is plotted along the left hand side versus redshift. The black scatter points indicate the mean halo mass for that redshift bin and the x indicate the median halo mass. The error bars indicate the 15.1\% and 84.1\% percentiles. Plotted along the right hand side is the percentage of halos that fall below the M01 mass threshold, also plotted along redshift. The M01 mass threshold (Eq. \ref{mthresh}), is plotted for the constant LW background in Eq. \ref{LWbg}. Almost all halos fall below the M01 relation, until $z$ = 12.5, when the mean halo mass rises above the relation.}
    \label{fig:mean_mass}
\end{figure}
